Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex

While our defaults termination condition quickly finds the correct lens for
\afm{35} of our \afm{45} benchmarks, our termination condition is not
one-size-fits all. Complex lenses, or lenses that project a
large amount of data, can be synthesized more easily and quickly by
adjusting $t$.
% end synthesis

@@

\subsection{Benchmark Suite}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill, though, of course, our tool produces bidirectional transformations rather than one-way transformers like Flash Fill.
\item We adapted \afm{29} benchmarks from Augeas. These benchmarks turn the
  ad hoc data present in Linux configuration files into a structured, dictionary
  representation.
\item We used \afm{8} benchmarks from synchronization tasks between a
  variety of real-life formats. These tasks range from synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

@@

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmark suite. \afm{8} of these
benchmarks had to be slightly altered to work with our new system. We altered
these benchmarks by either providing additional examples or tuning termination parameters.
Without these alterations, the symmetric synthesis yielded a lens that fit
the specification but that was not the desired lens.

@@

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 30 seconds, and averaged the result over 5 runs.
Figure~\ref{fig:times_bijective} summarizes the results of these tests. On
average, \SSOpt{} took 2.1 times (\afm{3.5} seconds) longer to complete than
\BSOpt{}. The slowest completed benchmark for both synthesis algorithms is
\texttt{xml\_to\_augeas.boom}, a benchmark that converts arbitrary XML up to
depth 3 into a serialized version of the structured dictionary representation
used in Augeas. This benchmark takes 18.9 seconds for the symmetric synthesis
algorithm to complete, and 9.3 seconds the bijective synthesis algorithm to
complete.

@@

We experimented with the \CCOpt{} mode to determine whether the complexity of the information theoretic measure was really needed. Related work on string transformations has often used simpler measures such as ``avoid constants'' which align with, but are simpler than our measures. The \CCOpt{} mode is an example of such a simple measure---it operates by counting disconnects, which put a complete stop to information transfer, like constants, and merges, which eliminate the information in a union. Figure~\ref{fig:metric} summarizes the result of this experiment. We find that
our metrics are very important for finding the correct lens. Our
information-theoretic metric is critical for finding the correct lens. Indeed,
only \afm{10} of our benchmarks succeeded when running in \CCOpt{} mode.

Our termination condition is also quite important. When running in \FLOpt{},
only \afm{5} lenses are found. The first cluster in which a lens is found is
rarely the correct cluster. However, our termination condition is not perfect.
Sometimes users must tell the algorithm to ``keep going'' or ``stop early.''
Without termination parameters, our algorithm finds the correct lens for 36 of
our 45 benchmarks, 9 of them need help in the form of a termination parameter
for finding the correct lens. That being said, our default parameter finds a
good middle-ground. Both \TFTOpt{} and \NTFTOpt{} synthesized the correct lens
less often than \ZTOpt.  \TFTOpt{} necessitates too good a lens, so the search
procedure keeps spinning, and \NTFTOpt{} terminates early, not finding the
correct lens.
% end evaluation

>>>>

While our defaults termination condition quickly finds the correct lens for
39 of our 48 benchmarks, our termination condition is not
one-size-fits all. Complex lenses, or lenses that project a
large amount of data, can be synthesized more easily and quickly by
adjusting $t$.
% end synthesis

@@

\subsection{Benchmark Suite}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted 8 data cleaning benchmarks from Flash Fill, though, of course, our tool produces bidirectional transformations rather than one-way transformers like Flash Fill.
\item We adapted 29 benchmarks from Augeas. These benchmarks turn the
  ad hoc data present in Linux configuration files into a structured, dictionary
  representation.
\item We used 11 benchmarks from synchronization tasks between a variety of
  formats taken from the bidirectional programming literature. These tasks range
  from synchronizing REST and JSON web resource descriptions to synchronizing
  BibTeX and EndNote citation descriptions.
\end{enumerate}

@@

To compare to the existing bijective synthesis algorithm, we run our symmetric
synthesis algorithm on the original Optician benchmark suite. 4 of these
benchmarks had to be slightly altered to work with our new system. We altered
these benchmarks by either providing additional examples or tuning termination parameters.
Without these alterations, the symmetric synthesis yielded a lens that fit
the specification but that was not the desired lens.

@@

For each benchmark in our benchmark suite, we ran every mode on it with a
timeout of 60 seconds, and averaged the result over 5 runs.
Figure~\ref{fig:times_bijective} summarizes the results of these tests. On
average, \SSOpt{} took 1.3 times (0.5 seconds) longer to complete than
\BSOpt{}. The slowest completed benchmark for both synthesis algorithms is
\texttt{xml\_to\_augeas.boom}, a benchmark that converts arbitrary XML up to
depth 3 into a serialized version of the structured dictionary representation
used in Augeas. This benchmark takes 18.9 seconds for the symmetric synthesis
algorithm to complete, and 9.3 seconds the bijective synthesis algorithm to
complete.

@@

We experimented with the \CCOpt{} mode to determine whether the complexity of the information theoretic measure was really needed. Related work on string transformations has often used simpler measures such as ``avoid constants'' which align with, but are simpler than our measures. The \CCOpt{} mode is an example of such a simple measure---it operates by counting disconnects, which put a complete stop to information transfer, like constants, and merges, which eliminate the information in a union. Figure~\ref{fig:metric} summarizes the result of this experiment. We find that
our metrics are very important for finding the correct lens. Our
information-theoretic metric is critical for finding the correct lens. Indeed,
only 10 of our benchmarks succeeded when running in \CCOpt{} mode.

Our termination condition is also quite important. When running in \FLOpt{},
only 5 lenses are found. The first cluster in which a lens is found is
rarely the correct cluster. However, our termination condition is not perfect.
Sometimes users must tell the algorithm to ``keep going'' or ``stop early.''
Without termination parameters, our algorithm finds the correct lens for 36 of
our 48 benchmarks, 9 of them need help in the form of a termination parameter
for finding the correct lens. That being said, our default parameter finds a
good middle-ground. Both \TFTOpt{} and \NTFTOpt{} synthesized the correct lens
less often than \ZTOpt.  \TFTOpt{} necessitates too good a lens, so the search
procedure keeps spinning, and \NTFTOpt{} terminates early, not finding the
correct lens.
% end evaluation
